{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-03-29 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, fixes

\begin{abstract} 
    Reports on papers read. 
    This is a LaTEX file for my own notes taking. 
    It may accelerate the process of writing my thesis for my PhD degree. 
    \todo{
        This is just pseudo text. This is just pseudo text. 
        This is just pseudo text. This is just pseudo text \cite{necoara_linear_2019}. 
    }
    \todoinline{This paper is currently in draft mode. Check source to change options. }
\end{abstract}
\chapter{The Basics of Optimization Theories}
    Notations in this chapter are not shared and they are for this chapter only.

@@

@@

            % NECOARA's ASSUMPTIONS ====================================================================================

@@

            \begin{definition}[Bregman Divergence]

@@

            % STRONG CONVEXITY DEFINITION ==============================================================================

@@

                There is no immediaet use of convexity besides that the projection $\bar x = \Pi_{X^+}x$ is a singleton.

@@

                Hence it gives the quadratic growth condition. 

@@

                However, it' still assumed in Necoara et al paper. 

@@

            The following theorems are about the relation between PEB and QFG. 
            \begin{theorem}{equivalence between QFG and PEB}

>>>>

\begin{abstract} 
    Reports on papers read. 
    This is a LaTEX file for my own notes taking. 
    It may accelerate the process of writing my thesis for my PhD degree. 
    \todo{
        This is just pseudo text. This is just pseudo text. 
        This is just pseudo text. This is just pseudo text \cite{necoara_linear_2019}. 
    \todoinline{This paper is currently in draft mode. Check source to change options. }
\end{abstract}
\chapter{The Basics of Optimization Theories}
    Notations in this chapter are not shared, and they are for this chapter only. 
    \begin{definition}[Bregman Divergence]\label{def:bregman-div}
    \begin{assumption}[smooth plus nonsmooth]\label{ass:smooth-add-nonsmooth}
        Let $F = f+ g$ where $f:\RR^n \rightarrow \overline \RR$ is differentiable and there exists $q\in \RR$ such that $g - q/2\Vert \cdot\Vert^2$ is convex.
    \begin{definition}[proximal gradient operator]
        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth}. 
        Define the proximal gradient operator by: 
            T_{\beta^{-1}, f, g}(x) &= \hprox_{\beta^{-1}g} \left(
                x - \beta^{-1} \nabla f(x)
            &= \argmin_{z}\left\lbrace
                g(z) + f(x) + \langle \nabla f(x), z - x\rangle
                + \frac{L}{2}\Vert x - z\Vert^2
            \right\rbrace. 
    % =================================================
    % WEAKLY CONVEX GENERIC PROXIMAL GRADIENT INEQUALITY
    % ==================================================
    \begin{theorem}[weakly convex generic proximal gradient inequality]\label{thm:pg-ineq-wcnvx-generic}\;\\
        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} with $\beta > 0$ and $q \in \RR$. 
        Then for all $x \in \RR^n, z \in \RR^n$, define $\bar x = T_{\beta^{-1}, f, g}(x)$, it has: 
            \frac{q}{2}\Vert z - x^+\Vert^2 
            &\le 
            F(z) - F(\bar x) - \langle \beta(x - \bar x), z - \bar x\rangle 
            + D_f(x, \bar x ) - D_f(z, x).  
        Nonsmooth analysis calculus rules has 
            \bar x &\in \argmin{z} \left\lbrace
                g(z) + \langle \nabla f(x), z\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
            \right\rbrace
            \implies
            \mathbf 0 
            &\in \partial g(x^+) + \nabla f(x) + \beta(x^+ - x)
            \partial g(x^+) &\ni
            - \nabla f(x) - \beta(x^+ - x). 
        The subgradient inequality for weak convexity has 
            \frac{q}{2}\Vert z - \bar x\Vert^2 
            &\le 
            g(z) - g(\bar x) + \langle \nabla f(x) + \beta(\bar x - x), z - \bar x\rangle
            g(z) - g(\bar x) + \langle \nabla f(x), z - \bar x\rangle + \langle \beta(\bar x - x), z - \bar x\rangle
            &= g(z) - g(\bar x) + \langle \nabla f(x), z - x\rangle
            + \langle \nabla f(x), x - \bar x\rangle
            + \langle \beta(\bar x - x), z - \bar x\rangle
            g(z) - g(\bar x) 
            + (-D_f(z, x) + f(z) - f(x))
            & \quad 
            + (D_f(\bar x, x) - f(\bar x) + f(x))
            + \langle \beta(\bar x - x), z - \bar x\rangle
            &= F(z) - F(\bar x) - D_f(z, x) + D_f(\bar x, x) 
            - \langle \beta(x - \bar x), z - \bar x\rangle. 
    \begin{theorem}[convex proximal gradient inequality]\label{theorem:pg-ineq}
        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} such that $q = \mu_g \ge 0$, $\beta \ge L_f$. 
        In addition, suppose that $f:\RR^n\rightarrow \RR$ has $L_f$ Lipschitz continuous gradient, and it's $\mu_f \ge 0$ strongly convex. 
        For all $x \in \RR^n, z \in \RR^n$, define $\bar x = T_{\beta^{-1}, f, g}(x)$ it has 
            0 &\le 
            F(z) - F(\bar x) + 
            \frac{\beta - \mu_f}{2}\Vert z - x\Vert^2
            - \frac{\beta + \mu_g}{2}\Vert z - \bar x\Vert^2. 
        The Bregman Divergence of $f$ has inequality 
            \left(\forall x \in \RR^n, y \in \RR^n\right)\; 
            \frac{\mu_f}{2}\Vert x - y\Vert^2 \le D_f(x, y) \le \frac{L_f}{2}\Vert x - y\Vert^2. 
        Specializing Theorem \ref{thm:pg-ineq-wcnvx-generic}, let $x \in \RR^n$ and define $\bar x = T_{\beta^{-1}, f, g}(x)$ it has $\forall z \in \RR^n:$
            \frac{\mu_g}{2}\Vert z - \bar x \Vert^2 
            &\le 
            F(z) - F(\bar x) 
            - D_f(z, x) + D_f(\bar x, x) 
            - \langle \beta(x - \bar x), z - \bar x\rangle
            &\le 
            F(z) - F(\bar x) 
            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
            + \frac{L_f}{2}\Vert x - \bar x\Vert^2
            - \langle \beta(x - \bar x), z - x + x - \bar x\rangle
            F(z) - F(\bar x) 
            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
            + \left(
                \frac{L_f}{2} - \beta
            \right)\Vert x - \bar x\Vert^2
            - \langle \beta(x - \bar x), z - x\rangle
            &\le 
            F(z) - F(\bar x) 
            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
            - \frac{\beta}{2}\Vert x - \bar x\Vert^2
            - \langle \beta(x - \bar x), z - x\rangle
            F(z) - F(\bar x) 
            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
            - \frac{\beta}{2}
            \left(
                \Vert x - \bar x\Vert^2
                + 2\langle x - \bar x, z - x\rangle
            F(z) - F(\bar x) 
            + \frac{\beta - \mu_f}{2}\Vert z - x\Vert^2 
            - \frac{\beta}{2}\Vert z - \bar x\Vert^2. 

@@

    In this section, $D_f$ will denote the Bregman Divergence as defined in Definition \ref{def:bregman-div}. 

@@

            % =======================
            % NECOARA's ASSUMPTIONS 
            % =======================

@@

@@

            % ==============================
            % STRONG CONVEXITY DEFINITION
            % ==============================

@@

                There is no immediate use of convexity besides that the projection $\bar x = \Pi_{X^+}x$ is a singleton.

@@

                Hence, it gives the quadratic growth condition. 

@@

                However, it' still assumed in Necoara et al. paper. 

@@

            Before we start, we will specialize Theorem \ref{theorem:pg-ineq} in our context because it will be used in later proofs. 
            In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
            In this case $\mu_g = 0$ and assuming $f$ is convex we have only $\mu_f = 0$. 
            Therefore the theorem specializes into the following inequality.

            \par
            The following theorems are about the relation between PEB and QFG. 
            \begin{theorem}[equivalence between QFG and PEB]
